### 2022-07-06 supplemental/OJEMB Supplementary Material.tex
Add new figure
Add to supplemental info

\begin{equation}
  m = 2595 \log_10 \bigg( 1 + \frac{f}{700} \big)
\end{equation}

@@

>>>>

\begin{equation}
  m = 2595 \log_10 \bigg( 1 + \frac{f}{700} \bigg)
\end{equation}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gfx/example_stimulus.eps}
	\caption{Example stimulus. \textbf{(a)} shows the waveform of the stimulus,
  \textbf{(b)} the frequency spectrum from which the waveform was generated,
  and \textbf{(c)} the $100$-dimensional bin representation.}
	\label{fig:examplestimulus}
\end{figure}

Furthermore, to reduce the system complexity by more than 80x,
we implement tonotopic binning, where the frequency scale is binned
along $100$ equally mel-spaced bins (Fig. \ref{fig:examplestimulus}).

\section{Hyperparameter Sweep}

To determine a suitable stimulus generation method,
we performed a hyperparameter sweep over hyperparameters
of nine different stimulus generation methods.
We used an \textit{in-silico} model of the experiment,
matching against an American Tinnitus Association tinnitus example,
as in the human experiment.

The methods are as follows:

\begin{enumerate}
  \item \textit{Bernoulli}: A binned method in which each tonotopic bin
  has a probability $p$ of being set to $0$ dB otherwise it is set to $-20$ dB.
  \item \textit{Brimijoin}: A binned method inspired by \cite{brimijoinInternalRepresentationVowel2013}.
  Each bin is assigned an amplitude value chosen from a uniform distribution of discrete values
  on the interval $[-20, 0]$. We used $6$ steps, which is consistent with the original paper.
  \item \textit{Gaussian Noise No Bins}: The amplitude of each frequency was determined by
  Gaussian noise with known mean and variance, which are hyperparameters $\mu$ and $\sigma$.
  \item \textit{Gaussian Noise}: A binned method where the bin amplitudes were
  determined by a Gaussian random variable with known mean and variance, \eg $\mathcal{N}(\mu, \sigma)$.
  \item \textit{Gaussian Prior}: A binned method where the number of filled bins
  was set by $\mathrm{round}(\mathcal{N}(\mu, \sigma))$,
  and that many bins were filled randomly at $0$ dB (unfilled bins were set to $-20$ dB).
  \item \textit{Power Distribution}: A binned method where the amplitude of each bin
  is drawn from a distribution matching the histogram of amplitudes
  of the American Tinnitus Association tinnitus examples from their website.
  \item \textit{Uniform Noise No Bins}: The amplitude associated with each frequency
  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
  \item \textit{Uniform Noise}: The amplitude associated with each tonotopic bin
  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
  \item \textit{Uniform Prior}: The number of filled bins is determined by drawing an integer
  from the discrete interval $[x_1, x_2] \in \mathbb{Z}^+$. Then, that many bins are set to $0$ dB,
  and all other bins are set to $-20$ dB. $x_1$ and $x_2$ are hyperparameters.
\end{enumerate}

9 methods and 8 hyperparameters were varied in the hyperparameter sweep grid search.
Methods were evaluated \textit{in-silico} using the model:

\begin{equation}
  y = \mathrm{sgn}(\Psi * \bar{x})
\end{equation}

where $y \in \mathbb{R}^n$ is the binary response vector,
$\Psi \in \mathbb{R}^{n \times d}$ is the stimulus matrix,
and $\bar{x} \in \mathbb{R}^d$ is the true target signal (the spectrum of the ATA tinnitus example).

Each stimulus generation method, with different hyperparameters,
was evaluated for target signals: buzzing, electric, roaring, screeching, static, and tea kettle.

\begin{table}[ht]
	\begin{center}	
		\small
		\resizebox{1\columnwidth}{!}{
			\begin{tabular}{ m{0.35\columnwidth} m{0.65\columnwidth} }	
				\multicolumn{2}{c}{\textsc{Units for Magnetic Properties}} \\
				\hhline{===}
				{Symbol} & {Quantity} \\
				\hhline{===}

			\end{tabular}
		}
	\end{center}
\end{table}

% n_bins: [10 30 100 200 300]
% bin_prob: [0.1000 0.3000 0.5000 0.8000]
% amplitude_mean: -35
% amplitude_var: [5 10 20]
% n_bins_filled_mean: [1 3 10 20 30]
% n_bins_filled_var: [0.0100 1 3 10]
% min_bins: [1 3 10 20 30]
% max_bins: [10 20 30 50]
